The Globular Cluster System of the Auriga Simulations

### 2019-03-22 AurigaGCS.tex
Bulletpointoutline of paragraph 0 of introduction

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
Globular clusters (GCs) are old, ubiquitous, and bright. 
GC ages range from $6-14$~Gyr, although observational age-estimates can be 
uncertain and a definitive age threshold to classify star clusters as `globular' 
remains topic of debate.
GCs are observed at scales ranging from clusters of galaxies down to 
dwarf galaxies 
The globular cluster system (GCS) of galaxy clusters can comprise 
a few hundred thousand GCs (citation needed), 
brightest cluster galaxies a few ten thousand (citation needed), 
spiral galaxies a few hundred (citation needed), 
and a handful GCs are expected to be present in dwarf galaxies with masses as low 
as $\sim10^{8}$~M\Sun (citation needed).

\todo[inline]{
    `The population of galaxies bound to a rich galaxy cluster can host 
    hundreds of thousands of GCs \citep{2013ApJ...775...20A}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    `brightest cluster galaxies can host tens of thousands 
    \citep{2008ApJ...681..197P, 2017ApJ...835..101H}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
}
\todo[inline]{
    `the Milky Way (MW) and M31 are known to host a few hundred
    \citep{1991ARA&A..29..543H}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    `Even at masses as low as $10^{8}$~M\Sun, the majority of galaxies still
    contain at least one GC \citep[e.g.][]{2010MNRAS.406.1967G}' 
    \citep[stolen from][]{2018MNRAS.475.4309P}
}

>>>>

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
\begin{itemize}
    \item old, ubiquitous, bright, `simple' single-age stellar populations
    \item properties (particularly metallicity) correlate with the host galaxy
    \item GCs can be used to understand galform, if GCform understood
\end{itemize}
Globular clusters (GCs) are old, ubiquitous, and bright. 
GC ages range from $6-14$~Gyr, although observational age-estimates can be 
uncertain and a definitive age threshold to classify star clusters as `globular' 
remains topic of debate.
GCs are observed at scales ranging from clusters of galaxies down to 
dwarf galaxies 
\todo[inline]{
    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
}
